Reproduction

### 2024-08-15 pages/reproduction.qmd
docs(reproduction): import from functions and add citations

**Shoaib and Ramamohan 2022:** This is a discrete-event simulation modelling primary health centres (PHCs) in India. There are four patient types: outpatients, inpatients, childbirth cases and antenatal care patients. Four model configurations are developed based on observed PHC practices or government-mandated operational guidelines. The paper explores different operational patterns for scenarios where very high utilisation was observed, to explore what might help reduce utilisation of these resources.

**Huang et al. 2019:** This is a discrete-event simulation model of an endovascular clot retrieval (ECR) service. ECR is a treatment for acute ischaemic stroke. The model includes the stroke pathway, as well as three other pathways that share resources with the stroke pathway: an elective non-stroke interventional neuroradiology pathway, an emergency interventional radiology pathway, and an elective interventional radiology pathway. The model is created using R Simmer. The paper explores waiting times and resource utilisation - particularly focussing on the biplane angiographic suite (angioINR). A few scenarios are tried to help examine why the wait times are so high for the angioINR.

**Lim et al. 2020:** This is a discrete-event simulation modelling the transmission of COVID-19 in laboratory. It examines the proportion of staff infected in scenarios varying the: number of shifts per day; number of staff per shift; overall staff pool; shift patterns; secondary attack rate of the virus; introduction of protective measures (social distancing and personal protective equipment). The model is created using Python.

**Kim et al. 2021:** This study adapts a previously developed discrete-event simulation model for abdominal aortic aneurysm (AAA) screening of men in England. It aims to explore different approaches to resuming screening and surgical repair for AAA, as these survives were paused or substantially reduced during COVID-19 due to concerns about virus transmission.

**Anagnostou et al. 2022:** This paper includes two models - we have focussed just on the dynamiC Hospital wARd Management (CHARM) model. CHARM is a discrete-event simulation modelling intensive care units (ICU) in the COVID-19 pandemic (as well as subsequent stays in a recovery bed). It includes three types of admission to the ICU (emergency, elective or COVID-19). COVID-19 patients are kept seperate, and if they run out of capacity due to a surge in COVID-19 admissions, additional capacity can be pooled from the elective and emergency capacity.

**Johnson et al. 2021:** TBC <!-- TODO: Add Johnson -->

@@

```{python}
# Import required libraries and functions
import matplotlib.pyplot as plt
import matplotlib.ticker as mtick
import numpy as np
import pandas as pd
from plotly import graph_objects as go
from time_to_complete import process_times, success_static, success_interactive

@@

>>>>

**@shoaib_simulation_2021:** This is a discrete-event simulation modelling primary health centres (PHCs) in India. There are four patient types: outpatients, inpatients, childbirth cases and antenatal care patients. Four model configurations are developed based on observed PHC practices or government-mandated operational guidelines. The paper explores different operational patterns for scenarios where very high utilisation was observed, to explore what might help reduce utilisation of these resources. *(Article published as @shoaib_simulation_2022, but we used the green open access pre-print)*

**@huang_optimizing_2019:** This is a discrete-event simulation model of an endovascular clot retrieval (ECR) service. ECR is a treatment for acute ischaemic stroke. The model includes the stroke pathway, as well as three other pathways that share resources with the stroke pathway: an elective non-stroke interventional neuroradiology pathway, an emergency interventional radiology pathway, and an elective interventional radiology pathway. The model is created using R Simmer. The paper explores waiting times and resource utilisation - particularly focussing on the biplane angiographic suite (angioINR). A few scenarios are tried to help examine why the wait times are so high for the angioINR.

**@lim_staff_2020:** This is a discrete-event simulation modelling the transmission of COVID-19 in laboratory. It examines the proportion of staff infected in scenarios varying the: number of shifts per day; number of staff per shift; overall staff pool; shift patterns; secondary attack rate of the virus; introduction of protective measures (social distancing and personal protective equipment). The model is created using Python.

**@kim_modelling_2021:** This study adapts a previously developed discrete-event simulation model for abdominal aortic aneurysm (AAA) screening of men in England. It aims to explore different approaches to resuming screening and surgical repair for AAA, as these survives were paused or substantially reduced during COVID-19 due to concerns about virus transmission.

**@anagnostou_facs-charm_2022:** This paper includes two models - we have focussed just on the dynamiC Hospital wARd Management (CHARM) model. CHARM is a discrete-event simulation modelling intensive care units (ICU) in the COVID-19 pandemic (as well as subsequent stays in a recovery bed). It includes three types of admission to the ICU (emergency, elective or COVID-19). COVID-19 patients are kept seperate, and if they run out of capacity due to a surge in COVID-19 admissions, additional capacity can be pooled from the elective and emergency capacity.

**@johnson_cost_2021:** TBC <!-- TODO: Add Johnson -->

@@

```{python}
# Import required libraries and functions
import matplotlib.pyplot as plt
import matplotlib.ticker as mtick
import numpy as np
import pandas as pd
from plotly import graph_objects as go
from functions import process_times, success_static, success_interactive

@@

## References
